The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-12 draft/ms.tex
First finalized table content and note.

  \colhead{Field\tablenotemark{a}} & \colhead{Data Type} & \colhead{Meaning} &
  \colhead{Related Fields\tablenotemark{b}} & \colhead{Ref.}

@@

OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of star & \nodata & \ref{sec:disc} \\

@@

T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{d} & -UPPER, etc. & W11 \\

@@

HJD\tablenotemark{d} & -UPPER, etc. & W11 \\

@@

HJD\tablenotemark{d} & -UPPER, etc. & \ref{sec:se} \\

@@

\tablenotetext{a}{Fields in bold are updates or new additions from
  \cite{Wright2011}. See Section~\ref{sec:update} for more details.}
\tablenotetext{b}{-UPPER etc. means ``-UPPER, -LOWER, U-, -REF, -URL",
where ``-" stands for the name of the field listed in the first
column. They are... See Section~\ref{sec:unc} and \ref{sec:ref} for
more details. -UL stands for upper limits for the fields (see

@@

\tablenotetext{c}{Originally as other commonly used name for star in \cite{Wright2011};
  changed to other commonly used name for planet.}
\tablenotetext{d}{The same as in \cite{Wright2011}, HJD/BJD etc.\ are
  still not consistent.}

>>>>

  \colhead{Field} & \colhead{Data Type} & \colhead{Meaning} &
  \colhead{Related Fields\tablenotemark{a}} & \colhead{Ref.\tablenotemark{b}}

@@

OTHERNAME\dotfill & String & Other commonly used name of star & \nodata & \ref{sec:disc} \\

@@

T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c} & -UPPER, etc. & W11 \\

@@

HJD\tablenotemark{c} & -UPPER, etc. & W11 \\

@@

HJD\tablenotemark{c} & -UPPER, etc. & \ref{sec:se} \\

@@

\tablenotetext{a}{``-UPPER etc." means ``-UPPER, -LOWER, U-, -REF,
  -URL", where ``-" stands for the name of the field listed in the
  first column. These fields store the uncertainties and
  references. See Section~\ref{sec:unc} and \ref{sec:ref} for more
  details. ``-UL" stands for upper limits for the fields (see

@@

\tablenotetext{b}{Fields that remain unchanged are referenced to
  \cite{Wright2011}, abbreviated as ``W11". Fields that are new or
  revised since \cite{Wright2011} are referenced to the relevant
  section in this paper.}
\tablenotetext{c}{As noted in \cite{Wright2011}, we do not report the
  epoches of periastron, transit center, and secondary eclipse center
  all consistently as HJD. We simply record what the original articles
  report, which are in varies formats (JD, BJD, HJD etc.).}
